\chapter{Conclusion and future works} % Main chapter title

\label{Chapter5 } % For referencing the chapter elsewhere, use \ref{Chapter1} 
\section{Conclusions}
In this study, contact problems with hyper-elastic materials are considered in cases of frictionless sliding and frictionless compressing and the obtained results are verified with the solution given by commercial program. From the theories and algorithms about contact problems and hyper – elastics materials based on finite element method, some programs are made to resolve the problem of contact for hyper–elastic materials. These example are programmed by using MATLAB programming languages, then the results which are gained from these programs are compared to the results of commercial program (ANSYS).
This study also compares displacement and stress results between 8-nodes element and 4-nodes element and shows the advantages of 8-nodes element.
\vspace{0.38cm}
\newline
But there are many disadvantages about this study, there are the solution programs only use Neo – Hookean model for material, the contact problems are only considered the frictionless behaviors and the results of the stress are less accurate.
\section{Future works}
In the future, this study have to be improved the algorithms to considered more material models, handle the frictional behavior of contact problems. By using more example to test the program, the failures may be found. So the program can be fixed where the failure are found, then the results will be improved.
\vspace{0.38cm}
\newline
Moreover, this study can be developed in reality problems such as three dimensions problems, dynamic problems,… There are many tasks which are very difficult and complicate, it need very much time and energy to complete all.